<!-- README.md is generated from README.rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# derappp - Data for Environmental Risk Assessment of Plant Protection Products

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)

```{r, results = "asis", echo = FALSE}
read.dcf("DESCRIPTION")[, "Description"] |> cat()
```

## Documentation

A good point to start is the vignette 
["Get Started"](https://agroscope-ch.github.io/derappp/articles/derappp.html)
in the online documentation. 

## Installation

You can install the current binary packages provided at R-Universe using:

```r
install.packages("derappp",
  repos = c(
    "https://agroscope-ch.r-universe.dev",  # For derappp and srppphist
    "https://jranke.r-universe.dev",        # For chents
    "https://cran.r-project.org"))
```

This will also install the dependencies [`chents`](https://pkgdown.jrwb.de/chents/) and [`srppphist`](https://agroscope-ch.github.io/srppphist/).

## Concept and scope

Please have a look a the
[concept](https://agroscope-ch.github.io/derappp/articles/concept.html)
for details.

