<!-- README.md is generated from README.rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

[![R-universe status](https://agroscope-ch.r-universe.dev/badges/derappp)](https://agroscope-ch.r-universe.dev/derappp)
[![R-CMD-check](https://github.com/agroscope-ch/derappp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/agroscope-ch/derappp/actions/workflows/R-CMD-check.yaml)

# derappp - Data for Environmental Risk Assessment of Plant Protection Products

```{r, results = "asis", echo = FALSE}
read.dcf("DESCRIPTION")[, "Description"] |> cat()
```

## Documentation

A good point to start is the vignette 
["Get Started"](https://agroscope-ch.github.io/derappp/articles/derappp.html)
in the online documentation. 

## Installation

You can install `derappp` from the Agroscope R-Universe using the command

```r
install.packages("derappp",
  repos = c(
    "https://agroscope-ch.r-universe.dev",
    "https://cran.r-project.org"))
```

This will also install the dependencies
[`chents`](https://pkgdown.jrwb.de/chents/) and
[`srppphist`](https://agroscope-ch.github.io/srppphist/) that
are not published on CRAN.

In case you wonder how to install a version <= 1.0.11 of the `DiagrammeR`
package (we list this as "Suggests:" in the DESCRIPTION), with the 
`pak` installed it is as easy as

```r
pak::pak("rich-iannone/DiagrammeR@v1.0.11")
```

## Concept and scope

Please have a look a the
[concept](https://agroscope-ch.github.io/derappp/articles/concept.html)
for details.

## Contribute

The easiest way to contribute data is to probably to prepare excel sheets
derived from those that can be found e.g. under
`data_generation/06_soil_sorption/` or `data_generation/10_aquatic_toxicity/`
and to upload them by navigating to the directory on github, and use the button
`Add file` and then select `Upload files`.

